---
title: "Employee earnings"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    css: styles.css
    navbar: 
      - { title: "REAL PAY", href: "real.html", align: right }
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(flexdashboard)
library(highcharter)
```

```{r prep_data}

charts_earnings <- readRDS("data/charts_earnings.rds")

```

The charts show median gross earnings of employees (without adjusting for inflation). Data is collected by the Office for National Statistics each April via the [Annual Survey of Hours and Earnings](https://www.ons.gov.uk/employmentandlabourmarket/peopleinwork/earningsandworkinghours/bulletins/annualsurveyofhoursandearnings/latest). The statistics cover employees only and exclude self-employed earnings.

# Weekly

These charts show weekly earnings.

## Column

### All employees

```{r}

charts_earnings$weekly_all

```

## Column {.tabset}

### Full-time employees

```{r}

charts_earnings$weekly_FT

```

### Part-time employees

```{r}

charts_earnings$weekly_PT

```

# Annual

These charts show annual earnings.

## Column

### All employees

```{r}

charts_earnings$annual_all

```

## Column {.tabset}

### Full-time employees

```{r}

charts_earnings$annual_FT

```

### Part-time employees

```{r}

charts_earnings$annual_PT

```

# Hourly

These charts show hourly earnings.

## Column

### All employees

```{r}

charts_earnings$hourly_all

```

## Column {.tabset}

### Full-time employees

```{r}

charts_earnings$hourly_FT

```

### Part-time employees

```{r}

charts_earnings$hourly_PT

```
