---
title: "Labour market indicators"
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(highcharter)
```

```{r prep_data}
charts_labourmarket <- readRDS("data/charts_labourmarket.rds")
rowheight <- 200
ncol <- 4
```

- **Employment rate** - The proportion of x year-olds who are employed or self-employed
- **Unemployment rate** - The proportion of x year-olds who are currently unemployed, i.e. they are looking for work
- **Inactivity rate** - The proportion of xx year-olds who are currently not employed or self-employed and are not actively looking for work.

The data is updated quarterly by the Office for National Statistics via the [Labour Force Survey](https://www.ons.gov.uk/employmentandlabourmarket/peopleinwork/employmentandemployeetypes/bulletins/regionallabourmarket/september2023). The shaded areas show measurement uncertainty (where available).

# Regions

```{r}
highcharter::hw_grid(charts_labourmarket$regions, 
                     ncol = ncol, rowheight = rowheight)
```

# Constituencies

## Row {.tabset .tabset-fade}

### Central Scotland {data-height=600}

```{r}
highcharter::hw_grid(
  charts_labourmarket$constituencies[["Central Scotland"]], 
  ncol = ncol, rowheight = rowheight)
```

### Glasgow

```{r}
highcharter::hw_grid(charts_labourmarket$constituencies[["Glasgow"]], 
                     ncol = ncol, rowheight = rowheight)
```

### Highlands and Islands

```{r}
highcharter::hw_grid(charts_labourmarket$constituencies[["Highlands and Islands"]],
                     ncol = ncol, rowheight = rowheight)
```

### Lothian

```{r}
highcharter::hw_grid(charts_labourmarket$constituencies[["Lothian"]], 
                     ncol = ncol, rowheight = rowheight)
```

### Mid Scotland and Fife

```{r}
highcharter::hw_grid(charts_labourmarket$constituencies[["Mid Scotland and Fife"]],
                     ncol = ncol, rowheight = rowheight)
```

### North East Scotland

```{r}
highcharter::hw_grid(charts_labourmarket$constituencies[["North East Scotland"]],
                     ncol = ncol, rowheight = rowheight)
```

### South Scotland

```{r}
highcharter::hw_grid(charts_labourmarket$constituencies[["South Scotland"]], 
                     ncol = ncol, rowheight = rowheight)
```

### West Scotland

```{r}
highcharter::hw_grid(charts_labourmarket$constituencies[["West Scotland"]], 
                     ncol = ncol, rowheight = rowheight)
```


