---
title: "Employee earnings in real terms"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    css: styles.css
    navbar: 
      - { title: "NOMINAL PAY", href: "index.html", align: right }

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(flexdashboard)
library(highcharter)
```

```{r prep_data}

charts_earnings <- readRDS("data/charts_earnings.rds")

```

The charts show median gross earnings of employees after adjusting for inflation. Data is collected by the Office for National Statistics each April via the [Annual Survey of Hours and Earnings](https://www.ons.gov.uk/employmentandlabourmarket/peopleinwork/earningsandworkinghours/bulletins/annualsurveyofhoursandearnings/latest). The statistics cover employees only and exclude self-employed earnings. We adjusted earnings using the [CPI inflator](https://www.ons.gov.uk/economy/inflationandpriceindices/bulletins/consumerpriceinflation/latest#latest-movements-in-cpi-inflation).

# Weekly

These charts show weekly earnings.

## Column

### All employees

```{r}

charts_earnings$weekly_all_real

```

## Column {.tabset}

### Full-time employees

```{r}

charts_earnings$weekly_FT_real

```

### Part-time employees

```{r}

charts_earnings$weekly_PT_real

```

# Annual

These charts show annual earnings.

## Column

### All employees

```{r}

charts_earnings$annual_all_real

```

## Column {.tabset}

### Full-time employees

```{r}

charts_earnings$annual_FT_real

```

### Part-time employees

```{r}

charts_earnings$annual_PT_real

```

# Hourly

These charts show hourly earnings.

## Column

### All employees

```{r}

charts_earnings$hourly_all_real

```

## Column {.tabset}

### Full-time employees

```{r}

charts_earnings$hourly_FT_real

```

### Part-time employees

```{r}

charts_earnings$hourly_PT_real

```
