---
title: "Pay"
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

```

```{r prep_data}
library(highcharter)
charts_earnings <- readRDS("data/charts_earnings.rds")
rowheight <- 300
ncol <- 3
```

# Nominal

The charts show median gross earnings of employees (without adjusting for inflation). Data is collected by the Office for National Statistics each April via the [Annual Survey of Hours and Earnings](https://www.ons.gov.uk/employmentandlabourmarket/peopleinwork/earningsandworkinghours/bulletins/annualsurveyofhoursandearnings/latest). The statistics cover employees only and exclude self-employed earnings.

## Weekly {data-height=300}

### All

```{r}
charts_earnings$weekly_all
```

### Full-time

```{r}
    charts_earnings$weekly_FT
```

### Part-time

```{r}
    charts_earnings$weekly_PT
```


## Annual {data-height=300}

### All

```{r}
charts_earnings$annual_all
```

### Full-time

```{r}
charts_earnings$annual_FT
```

### Part-time

```{r}
charts_earnings$annual_PT
```

## Hourly {data-height=300}

### All

```{r}
charts_earnings$hourly_all
```

### Full-time

```{r}
charts_earnings$hourly_FT
```

### Part-time

```{r}
charts_earnings$hourly_PT
```

# Real

The charts show median gross earnings of employees after adjusting for inflation. Data is collected by the Office for National Statistics each April via the [Annual Survey of Hours and Earnings](https://www.ons.gov.uk/employmentandlabourmarket/peopleinwork/earningsandworkinghours/bulletins/annualsurveyofhoursandearnings/latest). The statistics cover employees only and exclude self-employed earnings. We adjusted earnings using the [CPIH inflator](https://www.ons.gov.uk/economy/inflationandpriceindices/bulletins/consumerpriceinflation/latest#latest-movements-in-cpih-inflation).

## Weekly {data-height=300}

### All

```{r}
charts_earnings$weekly_all_real
```

### Full-time

```{r}
    charts_earnings$weekly_FT_real
```

### Part-time

```{r}
    charts_earnings$weekly_PT_real
```


## Annual {data-height=300}

### All

```{r}
charts_earnings$annual_all_real
```

### Full-time

```{r}
charts_earnings$annual_FT_real
```

### Part-time

```{r}
charts_earnings$annual_PT_real
```

## Hourly {data-height=300}

### All

```{r}
charts_earnings$hourly_all_real
```

### Full-time

```{r}
charts_earnings$hourly_FT_real
```

### Part-time

```{r}
charts_earnings$hourly_PT_real
```

