---
title: "Housing"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: rows
---
  
```{r setup, include = FALSE}

knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

```

```{r prep_data}

library(highcharter)
charts_housing <- readRDS("data/charts_housing.rds")

```

#### Housing statistics

- [Median house prices data is from Registers of Scotland](https://statistics.gov.scot/resource?uri=http%3A%2F%2Fstatistics.gov.scot%2Fdata%2Fresidential-properties-sales-and-price)
- Housing affordability uses the house price data above alongside [weekly median gross employee earnings data from the Annual Survey of Hours and Earnings](https://www.ons.gov.uk/employmentandlabourmarket/peopleinwork/earningsandworkinghours/datasets/annualsurveyofhoursandearningsasheguidetotables) 
- [Council tax data is from National Records of Scotland](https://statistics.gov.scot/data/dwellings-by-council-tax-band-detailed-current-geographic-boundaries)
- Tenure data is from the [Scottish Census 2011](https://www.scotlandscensus.gov.uk/search-the-census#/)

Further data: overcrowding (Census); social housing waitlists; house builidng; EPC data

# Central Scotland

## Row 1 {data-height=500}

### Median house prices

```{r}
charts_housing$house_prices[["Central Scotland"]]
```

### Housing affordability

```{r}
charts_housing$affordability[["Central Scotland"]]
```

## Row 2 {data-height=350}

### Tenure mix

```{r}
charts_housing$tenure_mix[["Central Scotland"]]
```

### Council tax mix

```{r}
charts_housing$counciltax[["Central Scotland"]]
```

## Row 3

### Median house prices over time

```{r}
charts_housing$house_prices_ts[["Central Scotland"]]
```

# Glasgow

# Highlands & Islands

# Lothian

# Mid Scotland & Fife

# North East Scotland

# South Scotland

# West Scotland

