---
title: "Housing"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: columns
---
  
```{r setup, include = FALSE}

knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

```

```{r prep_data}

library(highcharter)
charts_housing <- readRDS("data/charts_housing.rds")

```

#### Housing statistics

- Median house prices
- Housing affordability
- Council tax mix
- Tenure mix

# Central Scotland

## Column 1

### Median house prices {data-height=400}

```{r}
charts_housing$house_prices[["Central Scotland"]]
```

### Median house prices over time {data-height=400}

```{r}
charts_housing$house_prices_ts[["Central Scotland"]]
```

### Housing affordability {data-height=400}

## Column 2

### Tenure mix {data-height=600}

### Council tax mix {data-height=600}


# Glasgow

# Highlands & Islands

# Lothian

# Mid Scotland & Fife

# North East Scotland

# South Scotland

# West Scotland

