---
title: "SPICe statistics"
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
source("../R/functions/f_make_charts.R")

```

## Row 1 - by region

### Statistics

```{r}
flexdashboard::valueBox("Central Scotland", icon = "ion-stats-bars", 
                        color = spcols[7], href = "central_scotland.html")
```

### Statistics

```{r}
flexdashboard::valueBox("Glasgow", icon = "ion-stats-bars", color = spcols[7],
                        href = "glasgow.html")
```

### Statistics

```{r}
flexdashboard::valueBox("Highlands & Islands", color = spcols[7], 
                        icon = "ion-stats-bars",
                        href = "highlands_and_islands.html")
```

### Statistics

```{r}
flexdashboard::valueBox("Lothian", color = spcols[7], icon = "ion-stats-bars",
                        href = "lothian.html")
```

## Row 2 - by region

### Statistics

```{r}
flexdashboard::valueBox("Mid Scotland & Fife", color = spcols[7],
         icon = "ion-stats-bars", href = "mid_scotland_and_fife.html")
```

### Statistics

```{r}
flexdashboard::valueBox("North East Scotland", color = spcols[7],
         icon = "ion-stats-bars", href = "north_east_scotland.html")
```

### Statistics

```{r}
flexdashboard::valueBox("South Scotland", color = spcols[7],
         icon = "ion-stats-bars", href = "south_scotland.html")
```

### Statistics

```{r}
flexdashboard::valueBox("West Scotland", color = spcols[7],
         icon = "ion-stats-bars", href = "west_scotland.html")
```

## Row 3 - by topic

### Employment, Unemployment & Inactivity rates

```{r}
flexdashboard::valueBox("Labour market",
         color = spcols[2],
         icon = "ion-android-train",
         href = "labourmarket.html")
```

### Employee earnings

```{r}
flexdashboard::valueBox("Pay",
         color = spcols[2],
         icon = "ion-card",
         href = "earnings.html")
```


### House prices, affordability, tenure and council tax bands

```{r}
flexdashboard::valueBox("Housing",
         color = spcols[2],
         icon = "ion-home",
         href = "housing.html")
```

### Poverty

```{r}
flexdashboard::valueBox("Poverty",
         color = spcols[2],
         icon = "ion-ios-cart",
         href = "poverty.html")
```


### Health, disability and life expectancy

```{r}
flexdashboard::valueBox("Health",
         color = spcols[2],
         icon = "ion-ios-medkit",
         href = "health.html")
```

## Row 4 - UK nations

### UK nations

```{r}
flexdashboard::valueBox("Labour market",
         color = spcols[4],
         icon = "ion-android-train")
```

### UK nations

```{r}
flexdashboard::valueBox("Pay",
         color = spcols[4],
         icon = "ion-card",
         href = "earnings_nations.html")
```

### UK nations

```{r}
flexdashboard::valueBox("Housing",
         color = spcols[4],
         icon = "ion-home")
```

### UK nations

```{r}
flexdashboard::valueBox("Poverty",
         color = spcols[4],
         icon = "ion-ios-cart")
```

### UK nations

```{r}
flexdashboard::valueBox("Health",
         color = spcols[4],
         icon = "ion-ios-medkit")
```










