---
title: "Labour market indicators"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    orientation: columns
---
  
```{r setup, include = FALSE}

knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE
)

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

```

```{r prep_data}

library(highcharter)
charts_labourmarket <- readRDS("data/charts_labourmarket.rds")

```

- **Employment rate** - The proportion of 16-65 year-olds who are employed or self-employed
- **Unemployment rate** - The proportion of 16+ year-olds who are currently unemployed, i.e. they are looking for work
- **Inactivity rate** - The proportion of 16-65 year-olds who are currently not employed or self-employed and are not actively looking for work.

The data is updated quarterly by the Office for National Statistics via the [Labour Force Survey](https://www.ons.gov.uk/employmentandlabourmarket/peopleinwork/employmentandemployeetypes/bulletins/regionallabourmarket/september2023). The shaded areas show measurement uncertainty (where available). Missing data is shown as gaps. Due to small numbers, unemployment rates are not available on a constituency-level.

# Central Scotland

## Column 1

### Scottish Parliament Region {data-height=300 .first-box}

```{r}
charts_labourmarket$regions[["Central Scotland"]]
```

### Constituency {data-height=300}

```{r}
charts_labourmarket$constituencies[["Central Scotland"]][["Airdrie and Shotts"]]
```

### Constituency {data-height=300}

```{r}
charts_labourmarket$constituencies[["Central Scotland"]][["Coatbridge and Chryston"]]
```

### Constituency {data-height=300}

```{r}
charts_labourmarket$constituencies[["Central Scotland"]][["Cumbernauld and Kilsyth"]]
```

## Column 2

### Constituency {data-height=300}

```{r}
charts_labourmarket$constituencies[["Central Scotland"]][["East Kilbride"]]
```

### Constituency {data-height=300}

```{r}
charts_labourmarket$constituencies[["Central Scotland"]][["Falkirk East"]]
```

### Constituency {data-height=300}

```{r}
charts_labourmarket$constituencies[["Central Scotland"]][["Falkirk West"]]
```

### Constituency {data-height=300}

```{r}
charts_labourmarket$constituencies[["Central Scotland"]][["Hamilton, Larkhall and Stonehouse"]]
```

## Column 3

### Constituency {data-height=300}

```{r}
charts_labourmarket$constituencies[["Central Scotland"]][["Motherwell and Wishaw"]]
```

### Constituency {data-height=300}

```{r}
charts_labourmarket$constituencies[["Central Scotland"]][["Uddingston and Bellshill"]]
```

### empty {data-height=660 .empty-box .no-title}

# Glasgow

# Highlands & Islands

# Lothian

# Mid Scotland & Fife

# North East Scotland

# South Scotland

# West Scotland

