# `r stringr::str_replace("{{x}}", " and ", " & ")`

## Row 1 {data-height=350}

### {{x}} region {.first-box}

```{r}
charts_r[["{{x}}"]]
```

### {{x}} constituencies  - Employment {.first-box}

```{r}
charts_emp[["{{x}}"]]
```

### {{x}} constituencies - Inactivity {.first-box}

```{r}
charts_inact[["{{x}}"]]
```

## Row 2 {data-height=300}

### Constituency {.no-title}

```{r}
charts_c[["{{x}}"]][[1]]
```

### Constituency {.no-title}

```{r}
charts_c[["{{x}}"]][[2]]
```

### Constituency {.no-title}

```{r}
charts_c[["{{x}}"]][[3]]
```

## Row 3 {data-height=300}

### Constituency {.no-title}

```{r}
charts_c[["{{x}}"]][[4]]
```

### Constituency {.no-title}

```{r}
charts_c[["{{x}}"]][[5]]
```

### Constituency {.no-title}

```{r}
charts_c[["{{x}}"]][[6]]
```

## Row 4 {data-height=300}

### Constituency {.no-title}

```{r}
charts_c[["{{x}}"]][[7]]
```

### Constituency {.no-title}

```{r}
charts_c[["{{x}}"]][[8]]
```

### Constituency {.no-title}

```{r}
# using the try function means the code keeps running when we run out of constituencies in this region
try(charts_c[["{{x}}"]][[9]], silent = TRUE)
```

## Row 5 {data-height=300}

### Constituency {data-width=1}

```{r}
# using the try function means the code keeps running when we run out of constituencies in this region
try(charts_c[["{{x}}"]][[10]], silent = TRUE)

```

### Empty box {data-width=2 .no-title}
