## Row {.tabset}

### SIMD overall

<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:center;'>
<div>

```{r}

# flexbox code from https://github.com/rstudio/flexdashboard/issues/265

charts_deprivation$barchart[["SIMD"]][["{{x}}"]]
```

</div>
<div>

```{r}
charts_deprivation$region_maps[["SIMD"]][["{{x}}"]]
```

</div>
</div>

### Income domain

<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:center;'>
<div>

```{r}
charts_deprivation$barchart[["Income"]][["{{x}}"]]
```

</div>
<div>

```{r}
charts_deprivation$region_maps[["Income"]][["{{x}}"]]
```

</div>
</div>

### Employment domain

<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:center;'>
<div>

```{r}
charts_deprivation$barchart[["Employment"]][["{{x}}"]]
```

</div>
<div>

```{r}
charts_deprivation$region_maps[["Employment"]][["{{x}}"]]
```

</div>
</div>

### Health domain

<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:center;'>
<div>

```{r}
charts_deprivation$barchart[["Health"]][["{{x}}"]]
```

</div>
<div>

```{r}
charts_deprivation$region_maps[["Health"]][["{{x}}"]]
```

</div>
</div>

### Education domain

<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:center;'>
<div>

```{r}
charts_deprivation$barchart[["Education, Skills and Training"]][["{{x}}"]]
```

</div>
<div>

```{r}
charts_deprivation$region_maps[["Education, Skills and Training"]][["{{x}}"]]
```

</div>
</div>

### Housing domain

<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:center;'>
<div>

```{r}
charts_deprivation$barchart[["Housing"]][["{{x}}"]]
```

</div>
<div>

```{r}
charts_deprivation$region_maps[["Housing"]][["{{x}}"]]
```

</div>
</div>

### Crime domain

<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:center;'>
<div>

```{r}
charts_deprivation$barchart[["Crime"]][["{{x}}"]]
```

</div>
<div>

```{r}
charts_deprivation$region_maps[["Crime"]][["{{x}}"]]
```

</div>
</div>

### Access domain

<div style='display:flex; flex-direction:row; justify-content:space-evenly; align-items:center;'>
<div>

```{r}
charts_deprivation$barchart[["Access to Services"]][["{{x}}"]]
```

</div>
<div>

```{r}
charts_deprivation$region_maps[["Access to Services"]][["{{x}}"]]
```

</div>
</div>

## Row {data-height=300}

### Constituency {.no-title}

### Constituency {.no-title}

### Constituency {.no-title}

## Row {data-height=300}

### Constituency {.no-title}

### Constituency {.no-title}

### Constituency {.no-title}

## Row {data-height=300}

### Constituency {.no-title}

### Constituency {.no-title}

### Constituency {.no-title}

